---
output: github_document
---

  [![Travis build status](https://travis-ci.org/JiaxiangBU/add2todo.svg?branch=master)](https://travis-ci.org/JiaxiangBU/add2todo)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# add2todo

The goal of add2todo is to summarise the todo-list in the different documents.

## Installation

You can install the released version of add2todo from [Github](https://github.com/JiaxiangBU/add2todo) with:

```{r eval=F}
devtools::install_github('JiaxiangBU/add2todo')
```

```{r eval=F}
library(add2todo)
```

***

<h4 align="center">**Code of Conduct**</h4>

<h6 align="center">Please note that the 'add2md' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).<br>By contributing to this project, you agree to abide by its terms.</h6>

<h4 align="center">**License**</h4>

<h6 align="center">GPL-3 &copy; [Jiaxiang Li](LICENSE.md)</h6>
